The Chemistry Development Kit (CDK). 3. Atom typing, ...

### 2010-02-10 bmc_article.tex
Replaced demo material of template, with very rough outline of paper

\title{A sample article title}

@@

\author{Charles A Darwin\correspondingauthor$^{1,2}$%
       \email{Charles A Darwin\correspondingauthor - charles@londonzoo.co.uk}%
      \and
         Jane E Doe\correspondingauthor$^2$%
         \email{Jane E Doe\correspondingauthor - jane.e.doe@cambridge.co.uk}
       and 
         John RS Smith$^3$%
         \email{John RS Smith - john.RS.Smith@cambridge.co.uk}%
      }

@@

\address{%
    \iid(1)Life Sciences Department, Kings College London, Cornwall House,%
        Waterloo Road, London, UK\\
    \iid(2)Department of Zoology, Cambridge, Waterloo Road, London, UK\\
    \iid(3)Marine Ecology Department, Institute of Marine Sciences Kiel, %
        D\"{u}sternbrooker Weg 20, 24105 Kiel, Germany
}%

@@

%%%%%%%%%%%%%%%%
%% Background %%
%%
\section*{Background}
 Text for this section.\cite{koon,oreg,khar,zvai,xjon,schn,pond,smith,marg,hunn,advi,koha,mouse}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Results and Discussion %%
%%
\section*{Results and Discussion}
  \subsection*{Results sub-heading}
    \subsubsection*{This is a sub-sub-heading}
      Sub-sub-sub-headings are made with the \textsl{\\subsubsection} command. \pb
      pb at end of lines ensures correct paragraph spacing.\pb
	  Text for this sub-sub-section \ldots
    \subsubsection*{Another sub-sub-sub-heading}
      Text for this sub-sub-section \ldots

  \subsection*{Another results sub-heading}
    Text for this sub-section \ldots

  \subsection*{Yet another results sub-heading}
    Text for this sub-section.  More results \ldots

@@

%%%%%%%%%%%%%%%%%%
\section*{Methods}
  \subsection*{Methods sub-heading for this section}
    Text for this sub-section \ldots

  \subsection*{Another methods sub-heading for this section}
    Text for this sub-section \ldots

  \subsection*{Yet another sub-heading for this section}
    Text for this sub-section \ldots

@@

\section*{Figures}
  \subsection*{Figure 1 - Sample figure title}
      A short description of the figure content
      should go here.

  \subsection*{Figure 2 - Sample figure title}
      Figure legend text.

@@

%% Use of \listoftables is discouraged.
%%
\section*{Tables}
  \subsection*{Table 1 - Sample table title}
    Here is an example of a \emph{small} table in \LaTeX\ using  
    \verb|\tabular{...}|. This is where the description of the table 
    should go. \par \mbox{}
    \par
    \mbox{
      \begin{tabular}{|c|c|c|}
        \hline \multicolumn{3}{|c|}{My Table}\\ \hline
        A1 & B2  & C3 \\ \hline
        A2 & ... & .. \\ \hline
        A3 & ..  & .  \\ \hline
      \end{tabular}
      }
  \subsection*{Table 2 - Sample table title}
    Large tables are attached as separate files but should
    still be described here.

@@

\section*{Additional Files}
  \subsection*{Additional file 1 --- Sample additional file title}
    Additional file descriptions text (including details of how to
    view the file, if it is in a non-standard format or the file extension).  This might
    refer to a multi-page table or a figure.

  \subsection*{Additional file 2 --- Sample additional file title}
    Additional file descriptions text.

>>>>

\title{The Chemistry Development Kit (CDK). 3. Atom typing, ...}

@@

\author{
  Egon L Willighagen\correspondingauthor$^{1}$%
  \email{Egon L Willighagen\correspondingauthor - egon.willighagen@gmail.com}
\and
  Christoph Steinbeck\correspondingauthor$^2$%
  \email{Christoph Steinbeck\correspondingauthor - steinbeck@ebi.ac.uk}
}

@@

\address{
    \iid(1)Life Sciences Department, Kings College London, Cornwall House,
        Waterloo Road, London, UK\\
    \iid(2)Department of Zoology, Cambridge, Waterloo Road, London, UK
}

@@

%%%%%%%%%%%%%%%%
%% Background %%
%%
\section*{Background}

Open Source cheminformatics state \ldots (EGON)

Adoption of the CDK ... Cinfony~\cite{OBoyle2008}, and other bindings \ldots ...

Recent prominent use cases of the CDK~\cite{Steinbeck2003,Steinbeck2006} \ldots (EGON)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Results and Discussion %%
%%
\section*{Results and Discussion}

\subsection*{New Functionality}

Everyone is invited to contribute and write up the functionality they contributed;
only requirement: the code must have been incorporated into the main CDK library by the
time of submission of this paper.

  \subsubsection*{Atom Typing}

  The CDK has adopted a new atom typing algorithm \ldots (EGON)

\subsection*{Improved Coding Standards}

@@

%%%%%%%%%%%%%%%%%%
\section*{Methods}
  \subsection*{Peer Review: Automated}
    \subsubsection*{PMD}
    \subsubsection*{JavaDoc Checks}
  \subsection*{Peer Review: Manual}
  \subsection*{Unit Testing}

@@

%\section*{Figures}
%  \subsection*{Figure 1 - Sample figure title}
%      A short description of the figure content
%      should go here.
%
%  \subsection*{Figure 2 - Sample figure title}
%      Figure legend text.

@@

%% Use of \listoftables is discouraged.
%%
%\section*{Tables}
%  \subsection*{Table 1 - Sample table title}
%    Here is an example of a \emph{small} table in \LaTeX\ using  
%    \verb|\tabular{...}|. This is where the description of the table 
%    should go. \par \mbox{}
%    \par
%    \mbox{
%      \begin{tabular}{|c|c|c|}
%        \hline \multicolumn{3}{|c|}{My Table}\\ \hline
%        A1 & B2  & C3 \\ \hline
%        A2 & ... & .. \\ \hline
%        A3 & ..  & .  \\ \hline
%      \end{tabular}
%      }
%  \subsection*{Table 2 - Sample table title}
%    Large tables are attached as separate files but should
%    still be described here.

@@

%\section*{Additional Files}
%  \subsection*{Additional file 1 --- Sample additional file title}
%    Additional file descriptions text (including details of how to
%    view the file, if it is in a non-standard format or the file extension).  This might
%    refer to a multi-page table or a figure.
%
%  \subsection*{Additional file 2 --- Sample additional file title}
%    Additional file descriptions text.
